Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-01 paper/paper.tex
pass on related work

\Mar{mention something on ethical hacking.. ethical-hacking}

@@

\noindent
\textbf{Alternative methods for rule synthesis.} We discuss in the
following techniques similar in goal to ours. Unfortunately, we could
not access the tools implementing the techniques for side
comparison. Nevertheless, we found that there are important
differences between our work and related work. Vollmer
\etal{}~\cite{vollmer-etal-cics2011} propose the use of search to
derive rules for Snort, which are very similar to \suri's.  \Fix{Their
approach focuses on icmp attacks.} \Gui{The dataset used by them consists of manually produced ICMP packets using packet creation tools.}. It models every field of the icmp
packet in the chromosome of candidate solutions (\ie{}, a rule) of a
genetic search. The initial population is a set of candidate solutions
that randomly combine options, modelling the packet fields. They show
that they were able to generate rules without false negatives and only
3 false positives across 33K benign packets. The key differences
between our work and Vollmer~\etal{}'s are 1) the support of different
protocols and 2) the use of ranking to discriminate alternative
plausible rules. As for 1, our approach supports a variety of
protocols and options that refer to message payloads which
significantly increase the search space. The icmp rules they generate only
refer to message fields (see Section~\ref{sec:rules-and-packets}).
\MyComment{\Luc{eh possivel incluir contents em regras icmp tb. o q a secao 2.3 
diz q \textbf{geralmente} as regras nao-http possuem apenas field options}. }
As for 2, our solution additionally ranks plausible options, which
contain \emph{no} false positives or negatives with respect to the
benign and mallicious traffic considered.

\Gui{Guruprasad \etal{}\cite{guruprasad} also proposes an evolutionary framework, creating their own ICMP dataset as Vollmer, but also using DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets for non-ICMP attacks. The produced rules reported a detection rate up to 96\%. Although Guruprasad supports more protocols than Vollmer, our approach still supports more options and protocols, making both key differences considered when comparing with Vollmer also relevant with Guruprasad.}

Muthuregunathan \etal{}~\cite{muthuregunathan-etal2009} propose a clustering method to
create rules. They characterize candidate solutions as a set of field
values and use a clustering algorithm---hybrid k-means partitioned
around menoids---to isolate malicious from benign
traffic. Subsequently, they optimize the formed clusters using genetic
algorithms and hill-climbing search. Ou approach differs from theirs
in the method used, results, and support for content
options. Kao~\etal~\cite{Kao2015AutomaticNR} proposed ARGS, a system
to synthesize http rules that take malicious traffic as input. ARGS
looks for a common pattern across the different inputs to define
rules. It does not take existing rules as input or benign
traffic. Consequently, false positive can be produced and need to be
handled manually by users. Our approach, in contrast, does not
generate false positives w.r.t. the input traffic.

>>>>

%\Mar{mention something on ethical hacking.. ethical-hacking}

@@

%We discuss in the following techniques similar in goal to ours. Unfortunately

\noindent
\textbf{Alternative methods for rule synthesis.} As detailed before,
we could not access the tools implementing the techniques for
comparison. Nevertheless, we found that there are important
differences between our work and prior work. Vollmer
\etal{}~\cite{vollmer-etal-cics2011} proposed the use of search to
derive rules for Snort, which are very similar to \suri's.  Their
solution focused on icmp attacks for which plausible attacks can be
created directly from packets (see
Section~\ref{sec:rules-and-packets}). They modeled every field of the
icmp packet in chromosomes of candidate solutions (\ie{}, a rule) of a
genetic search. The initial population is a set of candidate solutions
that randomly combine options, modelling the packet fields. They
showed that they were able to generate rules without false negatives
and only 3 false positives across 33K benign packets. The key
differences between our work and Vollmer~\etal{}'s are 1) the support
of different protocols and 2) the use of ranking to discriminate
alternative plausible rules. As for 1, our approach supports a variety
of protocols and options (\eg{}, options that refer to message
payloads). The icmp rules they generate only refer to message fields.
\MyComment{\Luc{eh possivel incluir contents em regras icmp tb. o q a
    secao 2.3 diz q \textbf{geralmente} as regras nao-http possuem
    apenas field options}. } As for 2, our solution additionally ranks
plausible options, which contain \emph{no} false positives or
negatives with respect to the benign and mallicious traffic
considered. Guruprasad \etal{}\cite{guruprasad} also proposes an
evolutionary framework, creating their own ICMP dataset as Vollmer,
but also using DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx}
datasets for non-ICMP attacks. Although Guruprasad supports more
protocols than Vollmer, our approach still supports a larger set of
protocols and the ability to ranks rules. Muthuregunathan
\etal{}~\cite{muthuregunathan-etal2009} propose a clustering method to
create rules. They characterize candidate solutions as a set of field
values and use a clustering algorithm---hybrid k-means partitioned
around menoids---to isolate malicious from benign
traffic. Subsequently, they optimize the formed clusters using genetic
algorithms and hill-climbing search. Ou approach differs from theirs
in the method used, results, and support for content
options. Kao~\etal~\cite{Kao2015AutomaticNR} proposed ARGS, a system
to synthesize http rules that take malicious traffic as input. ARGS
looks for a common pattern across the different inputs to define
rules. It does not take existing rules as input or benign
traffic. Consequently, false positive can be produced and need to be
handled manually by users. Our approach, in contrast, does not
generate false positives w.r.t. the input traffic.

%% \Gui{Guruprasad \etal{}\cite{guruprasad} also proposes an evolutionary framework, creating their own ICMP dataset as Vollmer, but also using DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets for non-ICMP attacks. The produced rules reported a detection rate up to 96\%. Although Guruprasad supports more protocols than Vollmer, our approach still supports more options and protocols, making both key differences considered when comparing with Vollmer also relevant with Guruprasad.}
